Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures

### 2025-05-21 CCGRID Presentation/main.tex
added 2 pseudo columns on slide 23
KIT affiliation for Svetlana, et al. in footer

\author[S. Kulagina]{\underline{Svetlana Kulagina$^1$}, Anne Benoit$^2$ and Henning Meyerhenke$^{1,3}$}

@@

    % ——— content ———
    \vfill
    \begin{center}
    {\usebeamerfont{title}\usebeamercolor[fg]{title}\color{HUBblue}\LARGE\bfseries
    Memory-aware Adaptive Scheduling of Scientific Workflows\\
    On Heterogeneous Architectures\par}
                \vskip1.5em
            {\usebeamerfont{author}\usebeamercolor[fg]{author}\small
        \underline{Svetlana Kulagina$^1$}, Anne Benoit$^2$ and Henning Meyerhenke$^{1,3}$\par}
        \vskip1.5em

@@

    %\column{0.05\textwidth}
    \column{0.69\textwidth}
     \begin{figure}    
        \centering
         %\hskip -0.5cm
        \includegraphics[scale=0.3]{diagrams/images/schedulerAndRUntime.png}
        % \caption{Makespans of HomPart in comparison to HetPart1.}
    \end{figure}
    \column{0.29\textwidth}
   Runtime reports changes

@@

>>>>

\author[S. Kulagina et al.]{\underline{Svetlana Kulagina$^{1,3}$}, Anne Benoit$^2$ and Henning Meyerhenke$^{1,3}$}

@@

    % ——— content ———
    \vfill
    \begin{center}
    {\usebeamerfont{title}\usebeamercolor[fg]{title}\color{HUBblue}\LARGE\bfseries
    Memory-aware Adaptive Scheduling of Scientific Workflows\\
    On Heterogeneous Architectures\par}
                \vskip1.5em
            {\usebeamerfont{author}\usebeamercolor[fg]{author}\small
        \underline{Svetlana Kulagina}$^{1,3}$, Anne Benoit$^2$ and Henning Meyerhenke$^{1,3}$\par}
        \vskip1.5em

@@

    \column{0.05\textwidth}
    \column{0.69\textwidth}
     \begin{figure}    
        \centering
         %\hskip -0.5cm
        \includegraphics[scale=0.3]{diagrams/images/schedulerAndRUntime.png}
        % \caption{Makespans of HomPart in comparison to HetPart1.}
    \end{figure}
    \column{0.29\textwidth}
   Runtime reports changes

@@

    \end{itemize}
    \column{0.05\textwidth}
\end{columns}
